Hypertension and microbiome

### 2018-12-26 rrbiome.Rmd
Emacs

```{r libraries}

library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(finriskmetagcommon)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(ggpmisc)
library(Maaslin)

```{r functions, include = FALSE}

print.dset <- function(dset) {
    dset %>%
        gather(Covariate, Value) %>%
        group_by(Covariate) %>%
        summarise_all(., .funs = funs(mean(as.numeric(.), na.rm = TRUE),
                                         median(as.numeric(.), na.rm = TRUE),
                                         sd(as.numeric(.), na.rm = TRUE),
                                         min(as.numeric(.), na.rm = TRUE),
                                         max(as.numeric(.), na.rm = TRUE),
                                         NAs = sum(is.na(.)),
                                         n = n(),
                                         n_distinct)) %>%
            mutate_if(is.numeric, round, 2) %>%
            kable
}

@@

```{r data}

pseq <- readRDS("data/phfinrisk_genus_all_drop50k_2018-11-16.RDs")

@@

```{r variables}

data("phfinrisk_metadatadesc", package="finriskmetagcommon")
names.dset <- filter(phfinrisk_metadatadesc,
                     Ignored.Covariate.in.Cross.Sectional.Analysis.Aaro20181115==0)

@@

```{r filtering}

dset <- meta(pseq) %>%
    tibble::rownames_to_column(var = "rowname") %>%
    dplyr::select(rowname, DNA_OK, MEN, BL_AGE, SYSTM, DIASM, BP_TREAT, BMI, CURR_SMOKE, DIAB, BL_USE_RX_C09,
        Q57X, BL_USE_RX_C03, BL_USE_RX_C07, BL_USE_RX_C08) %>%
    dplyr::mutate(PULSEPRESSURE = SYSTM - DIASM,
                  HYPERTENSION = factor(ifelse(SYSTM >= 140 | DIASM >= 90 | BP_TREAT == 1, 1, 0)),
                  SEX = factor(ifelse(MEN == "Female", 1, 0)),
                  MAP = 2./3.*DIASM + 1./3.*SYSTM) %>%
    dplyr::select(-MEN) %>%
    stats::na.omit() %>%
    tibble::remove_rownames() %>%
    tibble::column_to_rownames(var = "rowname")

print.dset(dset)

@@

```{r Updating meta data}

pseq_filtered <- pseq
sample_data(pseq_filtered) <- sample_data(dset)

@@

>>>>

```{r libraries}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(finriskmetagcommon)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(ggpmisc)
library(Maaslin)
```

```{r functions, include = FALSE}
print.dset <- function(dset) {
    dset %>%
        gather(Covariate, Value) %>%
        group_by(Covariate) %>%
        summarise_all(., .funs = funs(mean(as.numeric(.), na.rm = TRUE),
                                         median(as.numeric(.), na.rm = TRUE),
                                         sd(as.numeric(.), na.rm = TRUE),
                                         min(as.numeric(.), na.rm = TRUE),
                                         max(as.numeric(.), na.rm = TRUE),
                                         NAs = sum(is.na(.)),
                                         n = n(),
                                         n_distinct)) %>%
            mutate_if(is.numeric, round, 2) %>%
            kable
}

@@

```{r data}
pseq <- readRDS("data/phfinrisk_genus_all_drop50k_2018-11-16.RDs")
```

@@

```{r variables}
data("phfinrisk_metadatadesc", package="finriskmetagcommon")
names.dset <- filter(phfinrisk_metadatadesc,
                     Ignored.Covariate.in.Cross.Sectional.Analysis.Aaro20181115==0)
```

@@

```{r filtering}
dset <- meta(pseq) %>%
    tibble::rownames_to_column(var = "rowname") %>%
    dplyr::select(rowname, DNA_OK, MEN, BL_AGE, SYSTM, DIASM, BP_TREAT, BMI, CURR_SMOKE, DIAB, BL_USE_RX_C09,
        Q57X, BL_USE_RX_C03, BL_USE_RX_C07, BL_USE_RX_C08) %>%
    dplyr::mutate(PULSEPRESSURE = SYSTM - DIASM,
                  HYPERTENSION = factor(ifelse(SYSTM >= 140 | DIASM >= 90 | BP_TREAT == 1, 1, 0)),
                  SEX = factor(ifelse(MEN == "Female", 1, 0)),
                  MAP = 2./3.*DIASM + 1./3.*SYSTM) %>%
    dplyr::select(-MEN) %>%
    stats::na.omit() %>%
    tibble::remove_rownames() %>%
    tibble::column_to_rownames(var = "rowname")

print.dset(dset)
```

@@

```{r Updating meta data}
pseq_filtered <- pseq
sample_data(pseq_filtered) <- sample_data(dset)
```

@@

```{r scp html}
system('scp rrbiome.html utu:articletwo')
```
